\huge A Usability Evaluation of Tor Launcher

### 2017-03-22 pets2017-paper/pets2017-paper.tex
Handle some of the recent todos:
-       Specifically, we describe how the initial evaluation --> delete “how”
-       Add conclusion section to roadmap at the end of introduction? Something like: we close with concluding remarks (section 11).
-       interview them about their experience after user --> after usage, or after the study
-       to establish or timeout --> time out (it’s the verb; not the noun)
-       interface for Tor had unique challenges --> has (since the challenges do not go away with this redesign)
-       4e, and 4h) --> visually there seems extra space in front of 4h; ta

Specifically, we describe how the initial evaluation of the interface (Section~\ref{sec:inspection}) and our observations of participants' interactions with it (Section~\ref{sec:qualitative}).
Based on the insights from our observations, we proposed several changes to the interface (Section~\ref{sec:design}) and measured how successfully and quickly users connect to Tor before and after changes (Section~\ref{sec:quantitative}).
Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address limitations of our evaluation (Section~\ref{sec:limitations}), and frame our study in the context of existing work (Section~\ref{sec:related}).
We hope that our usability evaluation serves as an informative case study and provides guidance on further improving Tor Launcher, as well as other privacy-enhancing technologies.

@@

We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user.
We recruited five participants per experimental condition to gather qualitative data; this has been suggested as the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}.
We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics.
We recruited twenty users per experimental condition to gather quantitative data, based on estimates of the number needed for statistical significance~\cite{howmanyusers}.

@@

\begin{itemize}
\item {\bfseries Completion rate:}  the percentage of users that want to connect to Tor and successfully do so. The higher the completion rate, the better. The ideal case would be that everyone is able to connect to Tor if they want to. Even if users do not successfully connect to Tor at first but eventually do so during the experiment, they are considered to have successfully connected to Tor for this metric.
\item {\bfseries Connection time:} the amount of time users take to connect to Tor. The less time it takes for users to connect, the better. The ideal case would be that the connection time is very close to the time it takes for the application to communicate with the servers and establish a circuit of relays for the connection, which can take up to several minutes. Connection time includes this bootstrapping time and any additional time that people spend in the interface.
\item {\bfseries Configuration time:} the amount of time users spend in the interface. The less time it takes for users to configure their preferences, the better. Configuration time is included in connection time, so it will always be less than connection time. We defined configuration time as any time spent on the bridge and proxy screens, since users were most likely configuring bridges and proxies. We excluded any time spent on the progress screen, because users were most likely waiting for connections to establish or timeout and not necessarily interacting with the interface. This should be as short as possible.
\end{itemize}

@@

Designing an interface for Tor had unique challenges: \\

@@

\begin{itemize}
\item{reduced the amount of text and technical terms in the text (Figures~\ref{fig:new-first},~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge},~\ref{fig:new-bridge-combobox}, and ~\ref{fig:new-progress})  to encourage users to read instructions.} 
\item{centered the text to make the design compatible for left to right and right to left languages.}
\item{clarified that configuration options were manual and for heavily censored environments (Figure~\ref{fig:new-first}) to discourage users who did not need bridges and proxies from configuring them.}
\item{added a status bar on the proxy and bridge screens (Figure~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge}, and~\ref{fig:new-bridge-combobox}) to hint at future tasks.}
\item{reordered proxy and bridge screens (Figures ~\ref{fig:new-proxy} and ~\ref{fig:new-nobridge}) in a topologically sequential order. This hints that proper proxy configuration is necessary to reach bridges.}
\item{eliminated the bridge and proxy questions (Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) to reduce the number of screens.}
\item{added auto-detection for proxies (Figure~\ref{fig:new-proxy}) in place of the proxy question. In theory, this can be done locally without infrastructural changes or leaking information to the network.}
\item{added the option to not use a bridge on the bridge screen (Figures~\ref{fig:new-nobridge}, ~\ref{fig:new-bridge} and ~\ref{fig:new-bridge-combobox}) to replace the function of the bridge question screen (Figure~\ref{fig:old-bridge}).}
\item{added a recommendation to use one of the three \texttt{meek}-transport bridges (Figure~\ref{fig:new-bridge}) if the recommended \texttt{obfs3}-transport bridges were unreachable, which happens in heavily censored real environments and our simulated environment E3.}
\item{added a summary screen (Figure~\ref{fig:new-summary}) that summarizes the settings before making a connection to Tor, since some participants from the previous study didn't know how they connected to Tor.}
\item{added indicators on the progress screen (Figure~\ref{fig:new-progress}) that visualized what components are trying to be reached, and in the case of failure, showed which component was unreachable. This was to help users understand what was going on during  connection and to help troubleshoot their configuration.}
\end{itemize}

>>>>

Specifically, we describe the initial evaluation of the interface (Section~\ref{sec:inspection}) and our observations of participants' interactions with it (Section~\ref{sec:qualitative}).
Based on the insights from our observations, we proposed several changes to the interface (Section~\ref{sec:design}) and measured how successfully and quickly users connect to Tor before and after changes (Section~\ref{sec:quantitative}).
Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address limitations of our evaluation (Section~\ref{sec:limitations}), frame our study in the context of existing work (Section~\ref{sec:related}),
and conclude (Section~\ref{sec:conclusion}).
We hope that our usability evaluation serves as an informative case study and provides guidance on further improving Tor Launcher, as well as other privacy-enhancing technologies.

@@

We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after use.
We recruited five participants per experimental condition to gather qualitative data; this has been suggested as the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}.
We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics.
We recruited twenty users per experimental condition to gather quantitative data, based on estimates of the number needed for statistical significance~\cite{howmanyusers}.

@@

\begin{itemize}
\item {\bfseries Completion rate:}  the percentage of users that want to connect to Tor and successfully do so. The higher the completion rate, the better. The ideal case would be that everyone is able to connect to Tor if they want to. Even if users do not successfully connect to Tor at first but eventually do so during the experiment, they are considered to have successfully connected to Tor for this metric.
\item {\bfseries Connection time:} the amount of time users take to connect to Tor. The less time it takes for users to connect, the better. The ideal case would be that the connection time is very close to the time it takes for the application to communicate with the servers and establish a circuit of relays for the connection, which can take up to several minutes. Connection time includes this bootstrapping time and any additional time that people spend in the interface.
\item {\bfseries Configuration time:} the amount of time users spend in the interface. The less time it takes for users to configure their preferences, the better. Configuration time is included in connection time, so it will always be less than connection time. We defined configuration time as any time spent on the bridge and proxy screens, since users were most likely configuring bridges and proxies. We excluded any time spent on the progress screen, because users were most likely waiting for connections to establish or time out and not necessarily interacting with the interface. This should be as short as possible.
\end{itemize}

@@

Designing an interface for Tor has unique challenges: \\

@@

\begin{itemize}
\item{reduced the amount of text and technical terms in the text (Figures~\ref{fig:new-first},~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge},~\ref{fig:new-bridge-combobox}, and~\ref{fig:new-progress})  to encourage users to read instructions.} 
\item{centered the text to make the design compatible for left to right and right to left languages.}
\item{clarified that configuration options were manual and for heavily censored environments (Figure~\ref{fig:new-first}) to discourage users who did not need bridges and proxies from configuring them.}
\item{added a status bar on the proxy and bridge screens (Figure~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge}, and~\ref{fig:new-bridge-combobox}) to hint at future tasks.}
\item{reordered proxy and bridge screens (Figures ~\ref{fig:new-proxy} and ~\ref{fig:new-nobridge}) in a topologically sequential order. This hints that proper proxy configuration is necessary to reach bridges.}
\item{eliminated the bridge and proxy questions (Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) to reduce the number of screens.}
\item{added auto-detection for proxies (Figure~\ref{fig:new-proxy}) in place of the proxy question. In theory, this can be done locally without infrastructural changes or leaking information to the network.}
\item{added the option to not use a bridge on the bridge screen (Figures~\ref{fig:new-nobridge}, ~\ref{fig:new-bridge} and ~\ref{fig:new-bridge-combobox}) to replace the function of the bridge question screen (Figure~\ref{fig:old-bridge}).}
\item{added a recommendation to use one of the three \texttt{meek}-transport bridges (Figure~\ref{fig:new-bridge}) if the recommended \texttt{obfs3}-transport bridges were unreachable, which happens in heavily censored real environments and our simulated environment E3.}
\item{added a summary screen (Figure~\ref{fig:new-summary}) that summarizes the settings before making a connection to Tor, since some participants from the previous study didn't know how they connected to Tor.}
\item{added indicators on the progress screen (Figure~\ref{fig:new-progress}) that visualized what components are trying to be reached, and in the case of failure, showed which component was unreachable. This was to help users understand what was going on during  connection and to help troubleshoot their configuration.}
\end{itemize}
